---
title       : Social Data Mining
subtitle    : Report
author      : Wolfgang Gross - Ramona Leenings
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## First Steps - Task 1

First we started with:

1. Looking at the Data
2. Decided to work with R
3. Find we need a preprocessing we couldn't do within R
4. Write a small programm reading and cleaning the raw dat in .NET Framework


---
## Data Cleaning

```{}
Dim sr As StreamReader = New StreamReader(inputpath + file)
Dim sw As StreamWriter = New StreamWriter(outputpath + file)

'Read every line
Dim line As String
line = sr.ReadLine()
```

---
## Data in R
Load and save Data
```{r,eval=FALSE}

dat_twelve <- fread('numeric_20140712.csv',header=F,sep=';')
saveRDS("numeric_20140712.Rda")
dat <- readRDS(file="numeric_20140712.Rda")
```

```{r,echo=FALSE,results='hide',message=FALSE}
library(ggplot2)
library(bit64)
dat1 <- readRDS(file="~/Documents/programmierung/Social Data Mining All/plot_second12.Rda")
dat2 <- readRDS(file="~/Documents/programmierung/Social Data Mining All/plot_minute12.Rda")
dat3 <- readRDS(file="~/Documents/programmierung/Social Data Mining All/plot_hour12.Rda")
dat4 <- readRDS(file="~/Documents/programmierung/Social Data Mining All/plot_minute13.Rda")
dat5 <- readRDS(file="~/Documents/programmierung/Social Data Mining All/plot_minute14.Rda")
```

---

## Working on the Data
```{r,eval=FALSE,}
count  <- data.frame(table(dat$V3))
count$Var1[1:5]
```

```{r,eval=FALSE,}
sumMinute <- c()
for(i in seq(1,length(count$Freq),60)){sumMinute <- append(sumMinute,sum(count$Freq[i:(i+60)]))}
sumHour <- c()
for(k in seq(1,length(count$Freq),3600)){sumHour <- append(sumHour,sum(count$Freq[k:(k+3600)]))}
realTime <- strptime(as.character(count$Var1),format="%Y%m%d%H%M%S")
Tweet.count <- count$Freq
```



---
## Plot the Data
```{r,eval=FALSE, fig.width=12,fig.height=6}
df <- data.frame(realTime,Tweet.count)
ggplot(df,aes(x=realTime,y=Tweet.count)) + geom_line()
```
```{r}
ggplot(dat1,aes(x=time,y=count)) + geom_line()
```

---
## Tweets per Second - Minute - Hour
Plot wiht different time resolutions

```{r,,echo=FALSE, fig.width=4,fig.height=6,warning=FALSE}
#plot tweets per second
ggplot(dat1,aes(x=time,y=count)) + geom_line()
#plot tweets per minute
ggplot(dat2,aes(x=time,y=count)) + geom_line()
#plot tweets per hour
ggplot(dat3,aes(x=time,y=count)) + geom_line()
```

---
## Tweets per Day
Plots for July the 12th - 13th - 14 | Tweets per minute

```{r,,echo=FALSE, fig.width=4,fig.height=6,warning=FALSE}
#plot tweets per second
ggplot(dat2,aes(x=time,y=count)) + geom_line()
#plot tweets per minute
ggplot(dat4,aes(x=time,y=count)) + geom_line()
#plot tweets per hour
ggplot(dat5,aes(x=time,y=count)) + geom_line()
```
